\documentclass[12pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{amssymb}

\hypersetup{
    colorlinks=true,
    linkcolor=black,
    urlcolor=blue,
}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[L]{\small Lease Agreement (Rev.\ %%%LEASE_REVISION%%%)}
\fancyfoot[R]{\small\thepage\ / \pageref{LastPage}}

% Run-in clause headings for the main body: "<n>. <Title>." flowing into the
% first paragraph (standard legal clause style).
\titleformat{\section}[runin]{\normalfont\bfseries}{\thesection.}{0.5em}{}[.\hspace{0.5em}]
\titlespacing*{\section}{0pt}{1.2em plus 0.3em minus 0.2em}{0.5em}
\titleformat{\subsection}[runin]{\normalfont\bfseries}{\thesubsection.}{0.5em}{}[.\hspace{0.5em}]
\titlespacing*{\subsection}{0pt}{0.8em plus 0.2em minus 0.1em}{0.5em}

% Unnumbered (starred) \subsection* keeps a display-style heading, used for the
% standalone disclosure form page where run-in numbering is inappropriate.
\titleformat{name=\subsection,numberless}{\normalfont\bfseries}{}{0em}{}
\titlespacing*{name=\subsection,numberless}{0pt}{1em plus 0.3em minus 0.2em}{0.3em}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.8em}

\begin{document}

\begin{center}
    {\small State of California \hfill %%%LEASE_HEADER_RIGHT%%%}

    \vspace{1em}
    {\Large\bfseries LEASE AGREEMENT}
\end{center}

\vspace{0.5em}

This Lease Agreement (this ``Agreement'') is made this %%%AGREEMENT_DATE%%%, by and between
\textbf{%%%LANDLORD_LEGAL_NAME%%%} (``Landlord'') and %%%TENANT_NAME%%% (``Tenant''). Each Landlord and
Tenant may be referred to individually as a ``Party'' and collectively as the ``Parties.''

\section{Premises}
The premises leased is %%%PREMISES_DESCRIPTION%%% located at %%%PREMISES_STREET%%%,
%%%PREMISES_CITY_STATE_ZIP%%% (the ``Premises'').

\section{Agreement to Lease}
Landlord agrees to lease to Tenant and Tenant agrees to lease from Landlord, according to the
terms and conditions set forth herein, the Premises.

\section{Term}
This Agreement will be for a term beginning on %%%TERM_START%%% and ending on %%%TERM_END%%%
(the ``Term'').

\section{Rent}
Tenant will pay Landlord a rent for the Term of %%%TOTAL_RENT_FOR_TERM%%% payable as follows: %%%PAYMENT_NOTE%%% in equal monthly
installments of %%%MONTHLY_RENT%%% (``Rent''). Rent will be payable in advance and due on the %%%RENT_DUE_DAY_OF_MONTH%%%
day of each month during the Term. Rent will be paid to Landlord at Landlord's address provided
herein (or to such other places as directed by Landlord) by mail or in person by one of the
following methods: %%%PAYMENT_METHODS%%%, and will be payable in U.S.\ Dollars.

\subsection{Initial Payments}
Upon execution of this Agreement by Tenant and as a condition of consideration for acceptance
by Landlord, Tenant shall pay to Landlord the following:

\begin{enumerate}[label=\Roman*.]
    \item The first rent payment.
    \item The Security Deposit. (See \S~\ref{sec:security-deposit})
\end{enumerate}

\section{Late Fee}
Rent paid after the %%%RENT_DUE_DAY_OF_MONTH%%% day of each month will be deemed as late; and if rent is not paid
within %%%LATE_GRACE_DAYS%%% day(s) after such due date, Tenant agrees to pay a late charge of %%%LATE_FEE_PERCENT%%%\% of
the balance due per month for each month that rent is late.

\section{Additional Rent}
There may be instances under this Agreement where Tenant may be required to pay additional
charges to Landlord. All such charges are considered additional rent under this Agreement and
will be paid with the next regularly scheduled rent payment. Landlord has the same rights and
Tenant has the same obligations with respect to additional rent as they do with rent.

\section{Utilities}
Tenant is responsible for payment of all utility and other services for the Premises, with the
exception of %%%UTILITIES_LANDLORD_COVERS%%%, which will be paid for or
provided by Landlord.

\section{Security Deposit}\label{sec:security-deposit}
Upon signing this Agreement, Tenant will pay a security deposit in the amount of %%%SECURITY_DEPOSIT%%%
to Landlord. The security deposit will be retained by Landlord as security for Tenant's
performance of its obligations under this Agreement. The security deposit may not be used or
deducted by Tenant as the last month's rent of the Term. Tenant will be entitled to a full
refund of the security deposit if Tenant returns possession of the Premises to Landlord in the
same condition as accepted, ordinary wear and tear excepted. Within thirty (30) days after the
termination of this Agreement, Landlord will return the security deposit to Tenant (minus any
amount applied by Landlord in accordance with this section). Any reason for retaining a
portion of the security deposit will be explained in writing. The security deposit will not bear
interest while held by Landlord in accordance with applicable state laws and/or local ordinances.

\section{Landlord's Failure to Give Possession}
In the event Landlord is unable to give possession of the Premises to Tenant on the start date
of the Term, Landlord will not be subject to any liability for such failure, the validity of this
Agreement will not be affected, and the Term will not be extended. Tenant will not be liable for
rent until Landlord gives possession of the Premises to Tenant. Notwithstanding anything to
the contrary, if Landlord does not deliver possession of the Premises within %%%POSSESSION_FAIL_MAX_DAYS%%% days of the
Start Date, Tenant may cancel this Agreement upon notice to Landlord and Landlord shall,
within %%%POSSESSION_REFUND_BUSINESS_DAYS%%% business days, return all monies paid by Tenant to Landlord.

\section{Holdover Tenancy}
If Landlord accepts a rent payment from Tenant, other than past due rent or additional rent,
after the Term expires, both Parties understand that a month-to-month holdover tenancy will be
created at the agreed upon monthly rent, unless proper notice has been served as required by
applicable laws. If either Tenant or Landlord wishes to end the month-to-month tenancy, such
Party must provide at least %%%HOLDOVER_NOTICE_DAYS%%% days' written notice before the desired termination
date.

\section{Use of Premises}
The Premises will be occupied only by Tenant and Tenant's immediate family and used only for
residential purposes. Tenant will not engage in any objectionable conduct, including behavior
which will make the Premises less fit to live in, will cause dangerous, hazardous or unsanitary
conditions or will interfere with the rights of others to enjoy their property. Tenant will be
liable for any damage occurring to the Premises and any damage to or loss of the contents
thereof which is done by Tenant or Tenant's guests or invitees. No guest of Tenant shall be
permitted to stay overnight at the Premises for more than twenty-one (21) nights in any
calendar month unless a separate written agreement regarding such guest's occupancy has been
executed by Landlord and Tenant.

\section{Condition of the Premises}
Tenant has examined the Premises, including the appliances and fixtures, and acknowledges that
they are in good condition and repair, normal wear excepted and tear, and accepts them in its
current condition.

\section{Maintenance and Repairs}
Tenant will maintain the Premises, including appliances and fixtures, in clean, sanitary and
good condition and repair. Tenant will not remove Landlord's appliances and fixtures from the
Premises for any purpose. If repairs other than general maintenance are required, Tenant will
notify Landlord for such repairs. In the event of default by Tenant, Tenant will reimburse
Landlord for the cost of any repairs or replacement.

\section{Reasonable Accommodations}
Landlord agrees to comply with all applicable laws providing equal housing opportunities,
including making reasonable accommodations for known physical or mental limitations of
qualified individuals with a disability, unless undue hardship would result. Tenant is
responsible for making Landlord aware of any such required accommodations that are reasonable
and will not impose an undue hardship. If Tenant discloses a disability and requests an
accommodation, Landlord has the right to have a qualified healthcare provider verify the
disability if the disability is not readily apparent, and Landlord has the right to use the
qualified healthcare provider verifying the disability as a resource for providing the
reasonable accommodation.

\section{Sex Offender Registry Notice}
Pursuant to Section 290.46 of the Penal Code, information about specified registered sex
offenders is made available to the public via an Internet website maintained by the Department
of Justice at \url{www.meganslaw.ca.gov}. Tenant understands and agrees that they are solely
responsible for obtaining any and all information contained in the state or national sex
offender registry for the area surrounding the Premises. Depending on an offender's criminal
history, this information will include either the address at which the offender resides or the
community of residence and zip code in which he or she resides.

\section{Compliance}
Tenant agrees to comply with all applicable laws, ordinances, requirements and regulations of
any federal, state, county, municipal or other authority.

\section{Mechanics' Lien}
Tenant understands and agrees that Tenant and anyone acting on Tenant's behalf does not have
the right to file for mechanic's liens or any other kind of liens on the Premises. Tenant
agrees to give actual advance notice to any contractors, subcontractors or suppliers of goods,
labor or services that such liens are invalid. Tenant further agrees to take the additional
steps necessary to keep the Premises free of any and all liens that may result from
construction completed by or for Tenant.

\section{Subordination}
With respect to the Premises, this Agreement is subordinate to any mortgage that now exists,
or may be given later by Landlord.

\section{Alterations}
Tenant will not make any alteration, addition or improvement to the Premises without first
obtaining Landlord's written consent. Any and all alterations, additions or improvements to
the Premises are without payment to Tenant and will become Landlord's property immediately on
completion and remain on the Premises, unless Landlord requests or permits removal, in which
case Tenant will return that part of the Premises to the same condition as existed prior to the
alteration, addition or improvement. Tenant will not change any existing locks or install any
additional locks on the Premises without first obtaining Landlord's written consent and without
providing Landlord a copy of all keys.

\section{Smoking}
Smoking of any kind is strictly prohibited on any part of the Premises. This prohibition
applies to Tenant and any visitors, guests or other occupants on the Premises.

\section{Pets}
Tenant is not allowed to have or keep any pets, even temporarily, on any part of the Premises.
The unauthorized presence of any pet will subject Tenant to penalties, damages, deductions
and/or termination of this Agreement. Properly trained service animals that provide assistance
to individuals with disabilities may be permitted on the Premises with the prior written
consent of Landlord, which shall not be unreasonably withheld. Tenant will be responsible for
the costs of de-fleaing, deodorizing and/or shampooing all or any portion of the Premises if a
pet has been on the Premises at any time during the Term (whether with or without written
consent of Landlord).

\section{Fire and Casualty}
If the Premises are damaged by fire or other serious disaster or accident and the Premises
becomes uninhabitable as a result, Tenant may immediately vacate the Premises and terminate
this Agreement upon notice to Landlord. Tenant will be responsible for any unpaid rent or will
receive any prepaid rent up to the day of such fire, disaster or accident. If the Premises are
only partially damaged and inhabitable, Landlord may make full repairs and will do so within a
prompt and reasonable amount of time. At the discretion of Landlord, the rent may be reduced
while the repairs are being made.

\section{Liability}
Landlord is not responsible or liable for any loss, claim, damage or expense as a result of
any accident, injury or damage to any person or property occurring anywhere on the Premises,
unless resulting from the gross negligence or willful misconduct of Landlord. Landlord encourages
Tenant to obtain renter's insurance to protect against loss of personal property and liability.

\section{Assignment and Subletting}
Tenant will not assign this Agreement as to any portion or all of the Premises or make or
permit any total or partial sublease or other transfer of any portion or all of the Premises.

\section{Insurance Requirements}
Tenant will not do or permit to be done any act or thing that will increase the insurance risk
under any policy of insurance covering the Premises. If the premium for such policy of
insurance increases due to a breach of Tenant's obligations under this Agreement, Tenant will
pay the additional amount of premium as additional rent under this Agreement.

\section{Right of Entry}
Landlord or its agents may enter the Premises at reasonable times to inspect the Premises, to
make any alterations, improvements or repairs or to show the Premises to a prospective tenant,
buyer or lender. In the event of an emergency, Landlord may enter the Premises at any time.

\section{Surrender}
Tenant will deliver and surrender to Landlord possession of the Premises immediately upon the
expiration of the Term or the termination of this Agreement, clean and in as good condition and
repair as the Premises was at the commencement of the Term, reasonable wear and tear excepted.

\section{Default}
In the event of any default under this Agreement, Landlord may provide Tenant a notice of
default and an opportunity to correct such default. If Tenant fails to correct the default,
other than a failure to pay rent or additional rent, Landlord may terminate this Agreement by
giving a %%%DEFAULT_NOTICE_DAYS%%% day written notice. If the default is Tenant's failure to timely pay rent
or additional rent as specified in this Agreement, Landlord may terminate this Agreement by
giving a %%%DEFAULT_NOTICE_DAYS%%% day written notice to Tenant. After termination of this Agreement, Tenant
remains liable for any rent, additional late, costs, including costs to remedy any defaults,
and damages under this Agreement.

\section{Remedies}
If this Agreement is terminated due to Tenant's default, Landlord may, in addition to any
rights and remedies available under this Agreement and applicable law, use any dispossession,
eviction or other similar legal proceeding available in law or equity.

\section{Subordination}
This Agreement and Tenant's right under it shall be subject and subordinate to the lien,
operation and effect of each existing or future mortgage, deed of trust, ground lease and/or
any other similar instrument of encumbrance covering any or all of the Premises, if any, and
each renewal, modification, consolidation, replacement or extension thereof.

\section{Condemnation}
If all or substantially all of the Premises are covered by a condemnation including the
exercise of any power of eminent domain by a governmental authority, this Agreement shall
terminate on the date possession of the Premises is taken by the condemning authority, and all
rent under this Agreement shall be prorated and paid to such date. Landlord is entitled to
collect from the condemning authority the entire amount of any award made in any proceeding.
Tenant waives any right, title or interest which Tenant may have to any such award and agrees
to not make any claim for the Term of this Agreement.

\section{Hazardous Materials}
Tenant shall not keep on the Premises any item of a dangerous, flammable, or explosive
character that might unreasonably increase the danger of fire or explosion on the Premises or
that might be considered hazardous or extra hazardous by any responsible insurance company.

\section{Lead Disclosure}
Housing built before 1978 may contain lead-based paint. Lead from paint, paint chips and dust
can pose health hazards if not managed properly. Lead exposure is especially harmful to young
children and pregnant women. Before renting pre-1978 housing, Landlord must disclose the
presence of known lead-based paint and/or lead-based paint hazards in the dwelling. Tenant
must also receive a federally approved pamphlet on lead poisoning prevention.

\section{Notices}
All notices given under this Agreement must be in writing. A notice is effective upon receipt
and shall be delivered in person, sent via certified or registered mail to the following
addresses (or to another address that either Party may designate upon reasonable notice to the
other Party):

Notices shall be sent to the Landlord at the following address:

\begin{quote}
    %%%LANDLORD_NOTICE_STREET%%%\\
    %%%LANDLORD_NOTICE_CITY_STATE_ZIP%%%\\
    Email: %%%LANDLORD_EMAIL%%%
\end{quote}

Notices shall be sent to the Tenant at the following address:

\begin{quote}
    %%%TENANT_NOTICE_STREET%%%\\
    %%%TENANT_NOTICE_CITY_STATE_ZIP%%%\\
    Email: %%%TENANT_EMAIL%%%
\end{quote}

\section{Quiet Enjoyment}
If Tenant pays the rent and performs all other obligations under this Agreement, Tenant may
peaceably and quietly hold and enjoy the Premises during the Term.

\section{No Waiver}
No Party shall be deemed to have waived any provision of this Agreement or the exercise of any
rights held under this Agreement unless such waiver is made expressly and in writing.

\section{Severability}
If any provision of this Agreement is held to be invalid, illegal or unenforceable in whole or
in part, the remaining provisions shall not be affected and shall continue to be valid, legal
and enforceable as though the invalid, illegal or unenforceable part had not been included in
this Agreement.

\section{Successors and Assigns}
This Agreement will inure to the benefit of and be binding upon the Parties and their permitted
successors and assigns.

\section{Governing Law}
The terms of this Agreement and the rights and obligations of the Parties hereto shall be
governed by and construed in accordance with the laws of the State of California, without
regard to its conflicts of laws provisions.

\section{Disputes}
Any dispute arising from this Agreement shall be resolved through mediation. If the dispute
cannot be resolved through mediation, then the dispute will be resolved through binding
arbitration conducted in accordance with the rules of the American Arbitration Association.

\section{Amendments}
This Agreement may be amended or modified only by a written agreement signed by the Parties.

\section{Counterparts}
This Agreement may be executed in one or more counterparts, each of which shall be deemed to
be an original, and all of which together shall constitute one and the same document.

\section{Headings}
The section headings herein are for reference purposes only and shall not otherwise affect the
meaning, construction or interpretation of any provision in this Agreement.

\section{Entire Agreement}
This Agreement constitutes the entire agreement between the Parties and supersedes and cancels
all prior agreements of the Parties, whether written or oral, with respect to the subject
matter.

\vspace{2em}

\begin{minipage}{\textwidth}
IN WITNESS WHEREOF, the Parties hereto, individually or by their duly authorized
representatives, have executed this Agreement as of the Effective Date, %%%AGREEMENT_DATE%%%.

\vspace{2em}

\textbf{LANDLORD:} %%%LANDLORD_LEGAL_NAME%%%

\vspace{3.5em}

\begin{tabular}{p{0.35\textwidth} p{0.45\textwidth} p{0.15\textwidth}}
                                 & %%%LANDLORD_SIGNATORY_NAME%%%, %%%LANDLORD_SIGNATORY_TITLE%%% & \\[-0.3em]
    \rule{0.32\textwidth}{0.4pt} & \rule{0.42\textwidth}{0.4pt}                                   & \rule{0.15\textwidth}{0.4pt} \\
    Landlord Signature           & Printed Name, Title                                            & Date \\
\end{tabular}

\vspace{2em}

\textbf{TENANT:}

\vspace{3.5em}

\begin{tabular}{p{0.35\textwidth} p{0.45\textwidth} p{0.15\textwidth}}
                                 & %%%TENANT_NAME%%%            & \\[-0.3em]
    \rule{0.32\textwidth}{0.4pt} & \rule{0.42\textwidth}{0.4pt} & \rule{0.15\textwidth}{0.4pt} \\
    Tenant Signature             & Printed Name                 & Date \\
\end{tabular}
\end{minipage}

\newpage

\begin{center}
    {\large\bfseries Disclosure of Information on Lead-Based Paint and/or\\
    Lead-Based Paint Hazards}
\end{center}

\vspace{1em}

\subsection*{Lead Warning Statement}

Housing built before 1978 may contain lead-based paint. Lead from paint, paint chips, and dust
can pose health hazards if not managed properly. Lead exposure is especially harmful to young
children and pregnant women. Before renting pre-1978 housing, lessors must disclose the
presence of known lead-based paint and/or lead-based paint hazards in the dwelling. Tenant
must also receive a federally approved pamphlet on lead poisoning prevention.

\subsection*{Landlord's Disclosure}

(a) Presence of lead-based paint and/or lead-based paint hazards (check (i) or (ii) below):

\begin{itemize}[label={}, leftmargin=1.5em]
    \item (i) \rule{0.5cm}{0.4pt} Known lead-based paint and/or lead-based paint hazard are
    present in the housing (explain):\par
    \rule{\linewidth}{0.4pt}\par
    \rule{\linewidth}{0.4pt}

    \item (ii) \underline{\ X\ } Lessor has no knowledge of lead-based paint and/or
    lead-based paint hazards in the housing.
\end{itemize}

(b) Records and reports available to the lessor (check (i) or (ii) below):

\begin{itemize}[label={}, leftmargin=1.5em]
    \item (i) \rule{0.5cm}{0.4pt} Lessor has provided the lessee with all available records
    and reports pertaining to the lead-based paint and/or lead-based paint hazards in the
    housing (list documents below):\par
    \rule{\linewidth}{0.4pt}\par
    \rule{\linewidth}{0.4pt}

    \item (ii) \underline{\ X\ } Lessor has no reports or records pertaining to lead-based
    paint and/or lead-based paint hazards in the housing.
\end{itemize}

\subsection*{Tenant's Acknowledgment}

(c) Tenant(s) who sign below acknowledge that they have received copies of all information
listed above.

(d) Tenant(s) who sign below acknowledge that they have received the pamphlet \textit{Protect
Your Family from Lead in Your Home}.

\subsection*{Certification of Accuracy}

The following Parties have reviewed the information above and certify, to the best of their
knowledge, that the information they have provided is true and accurate.

\vspace{2em}

\textbf{LANDLORD:} %%%LANDLORD_LEGAL_NAME%%%

\vspace{3.5em}

\begin{tabular}{p{0.35\textwidth} p{0.45\textwidth} p{0.15\textwidth}}
                                 & %%%LANDLORD_SIGNATORY_NAME%%%, %%%LANDLORD_SIGNATORY_TITLE%%% & \\[-0.3em]
    \rule{0.32\textwidth}{0.4pt} & \rule{0.42\textwidth}{0.4pt}                                   & \rule{0.15\textwidth}{0.4pt} \\
    Landlord Signature           & Printed Name, Title                                            & Date \\
\end{tabular}

\vspace{2em}

\textbf{TENANT:}

\vspace{3.5em}

\begin{tabular}{p{0.35\textwidth} p{0.45\textwidth} p{0.15\textwidth}}
                                 & %%%TENANT_NAME%%%            & \\[-0.3em]
    \rule{0.32\textwidth}{0.4pt} & \rule{0.42\textwidth}{0.4pt} & \rule{0.15\textwidth}{0.4pt} \\
    Tenant Signature             & Printed Name                 & Date \\
\end{tabular}

\end{document}
